Spatial Analysis

### 2021-05-25 Scripts/spatial_analisis.Rmd
Got the buffer

# Load it!
eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  filter(eez_name == "USA (East Coast)")

# ggplot(World_eez_sf) +
  # geom_sf()

@@

# us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
state_sf <-  st_read("~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb") %>% 
  janitor::clean_names() %>% 
  mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
  filter(jurisdicti %in% States)

@@

## Test with st_buffer

test <- state_sf %>% 
  filter(jurisdicti == "maine") %>% 
  select(jurisdicti,Shape)

ggplot(test) +
  geom_sf()

pbuf = st_buffer(test, 100)

p <- ggplot() +
  geom_sf(data = test, aes(), color = "blue") +
  geom_sf(data = pbuf, aes(), color = "red")

@@

### Test with library(ggforce)
# install.packages("ggforce")
library(ggforce)

 test <- state_sf %>% 
  filter(jurisdicti == "maine") %>% 
  select(jurisdicti,Shape)

>>>>

# Load it!
eez_sf <- st_read(dsn = path_world,
                        layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% #0.1
  filter(eez_name == "USA (East Coast)")

# ggplot(eez_sf) +
# geom_sf(aes(),fill =NA)

@@

# us_state_w <- rgdal::readOGR(dsn = "~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb")
state_sf <-  st_read("~/Downloads/FederalAndStateWaters/FederalAndStateWaters.gdb") %>% 
  janitor::clean_names() %>% 
  mutate(jurisdicti = str_to_lower(jurisdicti)) %>% 
  filter(jurisdicti %in% States) %>% 
  st_transform(crs = 4326) # for matching projections

@@

# Buffer state waters

state_bf = st_buffer(state_sf, 405000)

# ------------------------------ #
# Testing and visualizing the buffer 
# ------------------------------ #

# p <- ggplot() +
#   geom_sf(data = eez_sf, aes(), fill = NA) +
#   geom_sf(data = state_bf, aes(color = jurisdicti), fill = NA) +
#   geom_sf(data = state_sf, aes(color = jurisdicti), fill = NA)
#

# ggsave("testplotb.png",p)

# ------------------------------ #

#Join eez shapefile wih buffer

state_bf_ezz <- st_join(state_bf,eez_sf,join = st_contains)

pp <- ggplot(state_bf_ezz) +
  geom_sf()

@@
